---
title: "SUM demo"
author: "carljpearson"
date: "9/7/2018"
output: html_document
---

```{r setup, include=FALSE}

#method from MeasuringU.com https://measuringu.com/sum-2/

#load packages

library(tidyverse) #all data wrangling/plotting
library(psych) #just for the geometric averaging
library(knitr) #for rmarkdown
library(ggthemes) #tufte plots
library(shiny)

#preparation: here we get the data and add our own extra data like time specs and color choices for plots -----

  #get sample fake data -----

df <- structure(list(par = c(1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L, 3L, 3L, 
                             3L, 3L, 4L, 4L, 4L, 4L, 5L, 5L, 5L, 5L, 6L, 6L, 6L, 6L, 7L, 7L, 
                             7L, 7L, 8L, 8L, 8L, 8L, 9L, 9L, 9L, 9L, 10L, 10L, 10L, 10L, 11L, 
                             11L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, 14L, 
                             14L, 14L, 15L, 15L, 15L, 15L, 16L, 16L, 16L, 16L, 17L, 17L, 17L, 
                             17L, 18L, 18L, 18L, 18L, 19L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 
                             21L, 21L, 21L, 21L, 22L, 22L, 22L, 22L, 23L, 23L, 23L, 23L, 24L, 
                             24L, 24L, 24L, 25L, 25L, 25L, 25L, 26L, 26L, 26L, 26L, 27L, 27L, 
                             27L, 27L, 28L, 28L, 28L, 28L, 29L, 29L, 29L, 29L, 30L, 30L, 30L, 
                             30L, 31L, 31L, 31L, 31L, 32L, 32L, 32L, 32L, 33L, 33L, 33L, 33L, 
                             34L, 34L, 34L, 34L, 35L, 35L, 35L, 35L, 36L, 36L, 36L, 36L, 37L, 
                             37L, 37L, 37L, 38L, 38L, 38L, 38L, 39L, 39L, 39L, 39L, 40L, 40L, 
                             40L, 40L), task = c(1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 4L, 1L, 2L, 3L, 
                                                 4L, 1L, 2L, 3L, 4L), group = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                                                                                1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                                                                                1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                                                                                2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                                                                                2, 2, 2, 2, 2, 2, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                                                                                1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 
                                                                                1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                                                                                2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 
                                                                                2, 2, 2), comp = c(1L, 1L, 0L, 1L, 1L, 1L, 0L, 0L, 1L, 0L, 1L, 
                                                                                                   1L, 1L, 1L, 0L, 0L, 1L, 1L, 0L, 0L, 0L, 1L, 1L, 0L, 1L, 0L, 0L, 
                                                                                                   0L, 1L, 1L, 0L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 0L, 1L, 1L, 1L, 1L, 
                                                                                                   0L, 1L, 0L, 0L, 0L, 1L, 1L, 0L, 1L, 1L, 1L, 1L, 0L, 1L, 1L, 0L, 
                                                                                                   0L, 1L, 1L, 0L, 0L, 1L, 1L, 0L, 0L, 1L, 1L, 1L, 1L, 1L, 1L, 0L, 
                                                                                                   0L, 1L, 1L, 1L, 1L, 1L, 1L, 0L, 1L, 1L, 1L, 0L, 0L, 1L, 1L, 0L, 
                                                                                                   0L, 0L, 1L, 0L, 0L, 1L, 1L, 0L, 1L, 1L, 0L, 1L, 0L, 1L, 1L, 0L, 
                                                                                                   0L, 1L, 1L, 0L, 0L, 0L, 1L, 0L, 1L, 1L, 0L, 1L, 1L, 1L, 1L, 1L, 
                                                                                                   0L, 1L, 1L, 0L, 0L, 1L, 1L, 0L, 0L, 1L, 1L, 1L, 0L, 1L, 1L, 0L, 
                                                                                                   1L, 1L, 1L, 0L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 0L, 0L, 1L, 1L, 1L, 
                                                                                                   1L, 1L, 1L, 1L, 0L), sat = c(4.2, 4.4, 1.2, 4.4, 3.9, 3.9, 1.6, 
                                                                                                                                1, 4.2, 1.6, 3.9, 3.5, 4.7, 3.8, 2.3, 1.8, 3.6, 4.7, 1.4, 2.5, 
                                                                                                                                2.3, 4, 3.9, 1, 4.2, 1.9, 2.5, 1, 4.2, 4.4, 1.9, 3.5, 3.9, 3.9, 
                                                                                                                                4, 4.7, 3.9, 3.6, 2.5, 4.4, 4.4, 4.2, 4.3, 1.2, 4.4, 1.6, 1.2, 
                                                                                                                                2.7, 4.7, 4.2, 1.2, 4.6, 4.3, 3.6, 3.8, 1.2, 4.3, 3.6, 1, 1.6, 
                                                                                                                                3.8, 3.8, 1.6, 1.4, 3.5, 3.8, 1.4, 2.5, 4.4, 4, 4.7, 4.2, 3.9, 
                                                                                                                                3.9, 2.3, 1.6, 4.2, 3.5, 4.6, 3.6, 3.8, 4.4, 1, 3.9, 4.4, 3.6, 
                                                                                                                                2.3, 1.6, 3.9, 4.4, 1.2, 1.6, 1.4, 4, 2.7, 2.1, 4.4, 3.9, 1.4, 
                                                                                                                                4.4, 4.2, 2.1, 3.9, 1.8, 4.7, 3.9, 1, 1.6, 3.9, 4.3, 1.6, 2.5, 
                                                                                                                                2.1, 3.9, 2.1, 4.7, 4, 1.9, 4.6, 3.9, 3.8, 3.8, 3.5, 2.1, 4.6, 
                                                                                                                                4.2, 2.5, 1.9, 3.5, 4.2, 1.4, 1.9, 4.7, 3.5, 4, 2.5, 4.3, 4.2, 
                                                                                                                                1.6, 3.9, 4.6, 4, 2.5, 4.4, 4.2, 3.9, 4.6, 4, 4, 4.7, 2.7, 1.4, 
                                                                                                                                3.8, 4.2, 4.2, 3.8, 4.3, 4.2, 4.6, 1.6), time = c(30.5, 122.5, 
                                                                                                                                                                                  348.9, 726.7, 29.9, 140.9, 344.9, 606.2, 71.6, 51.4, 549.1, 667.2, 
                                                                                                                                                                                  84.1, 42.3, 796.6, 408.6, 38.7, 173.7, 715.7, 385.5, 75.9, 194.6, 
                                                                                                                                                                                  293.7, 311.9, 94.6, 204.9, 423.4, 464, 53.3, 155.1, 887.9, 451.4, 
                                                                                                                                                                                  64.3, 61.6, 909.5, 323.8, 42.6, 186.7, 348.9, 391.1, 65.4, 101.2, 
                                                                                                                                                                                  480.6, 623, 77.2, 122.8, 398.7, 931.3, 61.9, 67.3, 82.5, 838.1, 
                                                                                                                                                                                  30.4, 116.3, 487.2, 837.4, 87.6, 91.5, 379.3, 660.9, 93.1, 106.9, 
                                                                                                                                                                                  333.1, 801, 73.6, 125.2, 235.3, 694.5, 56.5, 62.6, 473.1, 999.3, 
                                                                                                                                                                                  29.7, 103.7, 216.4, 813.6, 56.5, 68.1, 496.5, 897, 64.1, 205.9, 
                                                                                                                                                                                  984.8, 535.4, 80.1, 109.9, 227.2, 726.7, 52.2, 218.4, 971.2, 
                                                                                                                                                                                  346.2, 45, 55.5, 925.5, 468.9, 66.6, 185.6, 260.1, 669.3, 52.6, 
                                                                                                                                                                                  175, 401, 965, 88.2, 155.9, 357, 702.9, 34.1, 111.5, 804.6, 431, 
                                                                                                                                                                                  89.8, 83.4, 532.3, 920.8, 32, 215.3, 495.5, 302.8, 52.9, 38.9, 
                                                                                                                                                                                  481.9, 309.1, 45.9, 31.2, 330.4, 866.9, 30.4, 129.2, 401.3, 741.4, 
                                                                                                                                                                                  28.3, 43.3, 299.2, 697.3, 82.5, 135.2, 456.4, 664.4, 53.8, 94.1, 
                                                                                                                                                                                  126.5, 700.1, 99.3, 33.1, 137.5, 621.6, 67.9, 93.8, 213.3, 508.8, 
                                                                                                                                                                                  95.2, 70.4, 155.6, 576.8, 82.6, 132.9, 112.9, 687.5)), .Names = c("par", 
                                                                                                                                                                                                                                                    "task", "group", "comp", "sat", "time"), row.names = c(NA, -160L
                                                                                                                                                                                                                                                    ), class = "data.frame")

  #renaming key SUM vars so we don't have to recode -----

colnames(df) #view col names to rename
df %>% rename(
  task=task, #task identifier
  par=par, #participant identifer
  time=time, #task time
  comp=comp, #task completion
  sat=sat #satisfaction average ratings
) -> df

#how many tasks did you test?
task_num <- 4

  #choose our z value

zval <- 1.64 #z value at 90% confidence, if you change, adjust plot subtitles

#color palette for plot
c(
  "#3B0083",
  "#00b9e4",
  "#007a87",
  "#ec7a08",
  "#92d400",
  "#f0ab00"
) -> colpal

  #get time specs

df %>% 
    filter(sat>=4) %>% #satisfaction above 4/5
    filter(comp==1) %>% #completed tasks only
    select(par,task,time) %>% #remove unneeded variables
    spread(task,time) %>% #widen data for loop of quantile calculation
    select(-par) -> time.quantiles #remove participant var and save
lapply(time.quantiles, quantile, #quantile function
       probs=seq(0, 1, by= 0.1), #provide sequence for granularity of quantiles
       name=FALSE, #no col names
       na.rm=T #remove NAs (sat < 4/5 and not completed)
       ) -> my_quants
names(my_quants) <- c(paste("Task",1:task_num)) #add col names
my_quants <- data.frame(my_quants) #make into a df


#use this plot to help specifiy your time spec
my_quants %>% 
  mutate(quantile=c(seq(0,1,by=.1))) %>% #provide quantile key variable
  gather(task,time,-quantile) %>% #elongate data
  mutate(quantile=as.factor(quantile)) -> my_quants_long #quantile needs to be factor for graphing, save
  ggplot(my_quants_long,aes(x=quantile,y=time,fill=quantile)) + #plot time across quantiles
  geom_bar(stat="identity") + #bar graph
  theme_minimal() +
  scale_fill_manual(values=c(rep("gray",8),"blue",rep("gray",2))) + #custom colors to make .8 bar stand out
  guides(fill=FALSE) + 
  scale_x_discrete(breaks=c(seq(0,1,by=.1)))+ #x axis ticks
  facet_wrap(~task, scales="free") #each task has its own plot



#manually add time specifications based on graph data or pre-existing product decisions
df$tspec[df$task==1] <- 60
df$tspec[df$task==2] <- 60
df$tspec[df$task==3] <- 120
df$tspec[df$task==4] <- 300
#df$tspec[df$task==5] <- 4
#df$tspec[df$task==6] <- 2



#data analysis: everything is now in place to begin to summarise and calculate -----
#NOTE THIS SCRIPT IS MADE HAVING ONLY ONE GROUP/VERSION/ETC 
#We will filter for a singleg group for now, but I plan to update this once I have all my real data with 2 versions
#df <- df %>% filter(group==1)

  #create completion df ----
df %>%
  group_by(group,task) %>% #group analyses broadly by product/version group and then by each task
  summarise(pass=sum(comp),n=n()) %>% #get n successes and n trials
  mutate(prop = pass / n) %>% #exact proportion from succesess/trials
  mutate(laplace = (pass + 1) / (n + 2)) %>% #laplace point estimate
  mutate(p_adj = (n * prop + (zval * zval) / 2) / (n + (zval * zval))) %>% #adjust p for wald calculation
  mutate(n_adj = n + (zval * zval)) %>% #adjust n for wald calculation
  mutate(marg =  zval * sqrt(p_adj * (1 - p_adj) / n_adj)) %>% #wald margin value
  mutate(lowerci = p_adj - marg) %>% #lower wald ci
  mutate(lowerci = ifelse(lowerci <= 0, 0, lowerci)) %>% #keep lower ci above 0
  mutate(upperci = p_adj + marg) %>% #upper wald ci
  mutate(upperci = ifelse(upperci >= 1, 1, upperci)) %>% #keep upper ci below 1
  mutate(point_est.z = laplace ) %>% #z score transform based on .78 baseline and bernouli variance
  mutate(lowerci.z= lowerci ) %>% #z score transform for conf intervals
  mutate(upperci.z = upperci ) %>% #z score transform for conf intervals
  mutate(point_est.nps=(point_est.z - .5) * 200)%>% #nps-ify
  mutate(lowerci.nps=(lowerci.z- .5 )* 200)%>% #nps-ify
  mutate(upperci.nps=(upperci.z- .5 )* 200)%>% #nps-ify
  rename(point.est=laplace) %>% mutate(Measure="Completion") %>% #name measure as var
  mutate(spec=.78 #define spec var for raw plots
  )-> df_comp

  #create satisfaction df -----
df %>%
  group_by(group,task) %>% #group analyses broadly by product/version group and then by each task
  na.omit() %>%
  summarise(mean=mean(sat),sd=sd(sat),n=n()) %>% #get means, std deviation, and total observations
  mutate(se=(sd / sqrt(n))) %>% #std error
  mutate(marg=se*zval) %>% #margin of error based on zval
  mutate(lowerci=mean-marg) %>% #lower ci
  mutate(lowerci = ifelse(lowerci <= 0, 0, lowerci)) %>% #keep lower ci above 0
  mutate(upperci=mean+marg) %>% #upper ci
  mutate(upperci = ifelse(upperci >= 5, 5, upperci)) %>% #keep upper ci below max
  mutate(point_est.z = pnorm((mean - 4)/sd)) %>% #z transform based on sd
  mutate(lowerci.z=pnorm((lowerci-4)/sd)) %>%  #z transform lower ci
  mutate(upperci.z=pnorm((upperci-4)/sd)) %>% #z transform upper ci
  mutate(point_est.nps=(point_est.z - .5) * 200) %>% #nps-ify
  mutate(lowerci.nps=(lowerci.z- .5 )* 200)%>% #nps-ify
  mutate(upperci.nps=(upperci.z- .5 )* 200)%>% #nps-ify
  mutate(Measure="Satisfaction") %>% #name measure as var
  mutate(spec=4) %>% #define spec var for raw plots
  rename(point.est=mean) -> df_sat

  #create time df -----
df %>%
  filter(comp==1) %>% #only completed tasks
  group_by(group,task,tspec) %>% #group analyses broadly by product/version group and then by each task, including task time spec
  summarise(mean=geometric.mean(time),sd = sd(time),n=n()) %>% #get mean, sd and n
  mutate(se=(sd / sqrt(n))) %>% #calculate std error
  mutate(marg=se*zval) %>% #calculate margin of error
  mutate(lowerci=mean-marg) %>% #lower ci
  mutate(lowerci = ifelse(lowerci <= 0, 0, lowerci)) %>% #keep lower ci above 0
  mutate(upperci=mean+marg) %>% #upper ci
  mutate(point_est.z = 1-pnorm((mean - tspec)/sd)) %>% #reverse proportion of z
  mutate(upperci.z=1-pnorm((lowerci-tspec)/sd)) %>% #upperci comes from lowerci after inversion
  mutate(lowerci.z=1-pnorm((upperci-tspec)/sd)) %>% #opposite as ^
  mutate(point_est.nps=(point_est.z - .5) * 200)%>% #nps-ify
  mutate(lowerci.nps=(lowerci.z- .5 )* 200)%>% #nps-ify
  mutate(upperci.nps=(upperci.z- .5 )* 200)%>%# nps-ify
  rename(point.est=mean,spec=tspec) %>% #rename some variables to fit into bind_rows
  mutate(Measure="Time") -> df_time

  #combining all dfs to sub measure summary
bind_rows(df_comp,df_sat,df_time) -> df_summarised #df from row bind
df_summarised$task <- as.factor(df_summarised$task)

#add better labels for task var, mainly used for plotting but function as factor variable
df_summarised$task_named[df_summarised$task==1] <- "Task 1: Start Function A"
df_summarised$task_named[df_summarised$task==2] <- "Task 2: Start Function B"
df_summarised$task_named[df_summarised$task==3] <- "Task 3: Combine Functions"
df_summarised$task_named[df_summarised$task==4] <- "Task 4: Debug"
#df_summarised$task_named[df_summarised$task==5] <- "Task 5: "
#df_summarised$task_named[df_summarised$task==6] <- "Task 6: "

  #Task level summaries from summarised df of submeasures
df_summarised %>% 
  group_by(group,task) %>% #keep product/versions separate, and only aggregate at task level
  summarise(point_est.z=mean(point_est.z), #average of point estimate std values
            lowerci.z=mean(lowerci.z), #average of lower CI std values
            upperci.z=mean(upperci.z), #average of upper CI std values
            point_est.nps=mean(point_est.nps), #average of pointe estimate NPS-like values
            lowerci.nps=mean(lowerci.nps), #average of lower CI NPS-like values
            upperci.nps=mean(upperci.nps) #average of upper CI NPS-like values
  ) %>%
  mutate(task=as.factor(task)
         )-> df_task
#add better labels for task var
df_task$task_named[df_task$task==1] <- "Task 1: Start Function A"
df_task$task_named[df_task$task==2] <- "Task 2: Start Function B"
df_task$task_named[df_task$task==3] <- "Task 3: Combine Functions"
df_task$task_named[df_task$task==4] <- "Task 4: Debug"
#df_task$task_named[df_task$task==5] <- "Task 5: "
#df_task$task_named[df_task$task==6] <- "Task 6: "

  #Overall SUM value
df_summarised %>%
  group_by(group) %>% #keep products separate
  summarise(point_est.z=mean(point_est.z), #average point estimates
            lowerci.z=mean(lowerci.z), #average lower CI
            upperci.z=mean(upperci.z)) %>% #average upper CI
  data.frame() %>% 
  group_by(group) %>%
  summarise(mean=mean(point_est.z), 
            sd=sd(point_est.z),
            n=n(),
            lowerci.z=mean(lowerci.z),
            upperci.z=mean(upperci.z)) %>%
  mutate(se=(sd / sqrt(n))) %>%
  mutate(marg=se*zval) %>%
  mutate(lowerci.grand=mean-marg) %>%
  mutate(lowerci.grand = ifelse(lowerci.grand <= 0, 0, lowerci.grand)) %>%
  mutate(upperci.grand=mean+marg) %>%
  mutate(upperci.grand = ifelse(upperci.grand >= 5, 5, upperci.grand)) %>%
  mutate(group=as.factor(group)) %>%
  rename(point_est.z=mean)%>%
  mutate(point_est.nps=(point_est.z - .5) * 200)%>%
  mutate(lowerci.nps=(lowerci.z- .5 )* 200)%>%
  mutate(upperci.nps=(upperci.z- .5 )* 200) %>%
  select(group=group,
         final_SUM=point_est.nps,
         final_SUM_low=lowerci.nps,
         final_SUM_hi=upperci.nps,
         final_SUM_perc=point_est.z,
         final_SUM_perc_low=lowerci.z,
         final_SUM_perc_hi=upperci.z
         ) -> df_SUM


```

## Single Usability Metric (SUM) Script Demo

The [SUM method](https://measuringu.com/sum-2/) follows a classic usability testing protocol of metrics collection across tasks. The novelty of the SUM lies in its combination of those metrics through standardized values. This R Markdown document shows the outputs of the script, both data tables and the resulting plots. The [script in its raw form can be found here.](https://github.com/carljpearson/sum_calc_example)

 The data are all simulated with heuristically plausible relationships between all sub-measures. If you use the script, it's easy to drop your own data in (be sure it's in [long](http://www.cookbook-r.com/Manipulating_data/Converting_data_between_wide_and_long_format/) format). The script will point out where you need to rename variables. You need to be sure time measures are in seconds, completion is binary, and satisfaction should be on a 1-5 scale. It should look like the table below once you're done.

```{r df, echo=FALSE}
kable(head(df))
```

### What happens after all these individual lines

####The script calculates all sub-task raw measures. 

* **Task completion**
    + LaPlace point estimates
    + Adjusted Wald confidence intervals
* **Time-on-task** for completed tasks only
  + Geometric average point estimates (to help account for skew)
  + Standard confidence intervals
* **Satisfaction** 
  + Standard average point estimates
  + Standard confidence intervals

####To make it into the SUM, all values are standardized based on a benchmark value.

* **Task completion**
  + Converted directly to percentage value based on the pnorm() function
  + (A good benchmark is .78, but small samples make it tough to approximate a z-score)
* **Time-on-task** for completed tasks only
  + You enter the time you aim for all users to complete the task by to get benchmarks
  + Converted to z-score and then percentage equivalent
* **Satisfaction** 
  + We use a standard benchmark of 4/5 for 'good' usability
  + Converted to z-score and then percentage equivalent
  
To make it more accesible to non-researchers, I translate the percentage to an **NPS like score of -100 to 100**. Here's what your summarized (or summari*s*ed, if you're using dplyr) table looks like:

```{r echo=FALSE}
df_summarised %>%
  select(
    'Group' = group,
    "Task" = task,
    'Raw point estimate' = point.est,
    'Raw lower confidence' = lowerci,
    'Raw upper confidence' = upperci,
    'NPS point estimate' = point_est.nps,
    'NPS lower confidence' = lowerci.nps,
    'NPS upper confidence' = upperci.nps
    
  ) %>% head() %>% kable(caption="Selected example columns/rows",digits = 2)
```

####Next we average the NPS-like values to get our task level SUM scores.

```{r echo=FALSE}
df_task %>%
  select(
    'Group' = group,
    "Task" = task,
    'NPS point estimate' = point_est.nps,
    'NPS lower confidence' = lowerci.nps,
    'NPS upper confidence' = upperci.nps
    
  ) %>% kable(caption="Selected example columns",digits = 2)
```

####We quickly come to our final SUM values.

```{r echo=FALSE}
df_SUM %>%
  select(
    'Group' = group,
    final_SUM,
         final_SUM_low,
         final_SUM_hi
    
  ) %>% kable(caption="Selected example columns",digits = 2)
```

####For our final SUM scores, a table works well because we have just a few data points. For everything else, we may want some plots.

#Plotting

###First up, we can plot our data for each group (version) individually. This is helpful when you want to review how the first round of testing went (version 1, product 1, etc).

###**Raw task** metrics show the data before any transformation.

```{r include=FALSE}

#completion
df_summarised %>% 
  filter(group==1) %>% #choose grouping
  filter(Measure=="Completion") %>% #only completion
  ggplot(aes(x=task, y=point.est,ymin=lowerci, ymax=upperci, fill=task_named)) +  #vars to be plotted
  geom_bar(position=position_dodge(), stat="identity") + #make a bar plot with color palette
  geom_abline(intercept=.78,slope=0, color = "gray",linetype = 2, size=2) + #horizontal benchmark line
  coord_cartesian(ylim=c(0,1)) + #limit y axis between 0-1
  geom_errorbar(position=position_dodge(), stat="identity",color="darkgray",width=.2) + #error bar geom and sizing
  scale_y_continuous(labels = scales::percent) + #make y labels in percentage
  labs(x="Task", y="Estimated proportion") + #explicit axis labels
  ggtitle(label = "Estimated completion rates across all tasks", #title of graph
          subtitle = "Confidence intervals at 90%, gray line indicates benchmark") + #subtitle of graph
  ggthemes::theme_tufte(base_family="GillSans") + #tufte theming (max dataink) with sans serif font
  scale_fill_manual(values=colpal)+
  guides(fill=guide_legend(title="Task Legend"))+
  theme(
    axis.text.x = element_text(size = 15)
    ) -> p.comp_raw

#satisfaction
df_summarised %>%
  filter(group==1) %>%
  filter(Measure=="Satisfaction") %>%
  ggplot(aes(x=task, y=point.est,ymin=lowerci, ymax=upperci,fill=task_named)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_abline(intercept=4,slope=0, color = "gray",linetype = 2, size=2)+
  coord_cartesian(ylim=c(1,5)) +
  geom_errorbar(position=position_dodge(), stat="identity",color="darkgray",width=.2) +
  labs(x="Task", y="Satisfaction score") +
  ggtitle(label = "Average satisfaction measure scores across all tasks",
          subtitle = "Confidence Intervals at 90%, gray line indicates benchmark") +
  guides(fill=FALSE) +
  ggthemes::theme_tufte(base_family="GillSans") + 
  scale_fill_manual(values=colpal)+
  guides(fill=guide_legend(title="Task Legend"))+
  theme(
    axis.text.x = element_text(size = 15),
    axis.title.x = element_blank()
    ) -> p.sat_raw #save object

#time
df_summarised %>%
  filter(group==1) %>%
  filter(Measure=="Time") %>%
  group_by(task) %>%
  ggplot(aes(x=task, y=point.est,fill=task_named,ymin=lowerci, ymax=upperci)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymax=spec,ymin=spec),position=position_dodge(), stat="identity", color = "#3C3C3C",linetype = 2, size=2)+
  #coord_cartesian(ylim=c(0,1)) +
  geom_errorbar(position=position_dodge(), stat="identity",color="darkgray",width=.2) +
  labs(x="Task", y="Time geometric average in seconds") +
  ggtitle(label = "Raw time averages across all tasks",
          subtitle = "Confidence Intervals at 90%, gray lines indicate benchmark") +
  #scale_y_time(labels=date_labels("%M $S"))+
  facet_grid(.~task, scales="free")+
  ggthemes::theme_tufte(base_family="GillSans") + 
  scale_fill_manual(values=colpal)+
  guides(fill=guide_legend(title="Task Legend"))+
  theme(
    axis.text.x = element_text(size = 15),
    axis.title.x = element_blank(),
    legend.position="none",
    strip.background = element_blank(), #remove face label area
    strip.text.x = element_blank() #remove facet label text
  ) -> p.time_raw
```


```{r echo=FALSE}
plot(p.comp_raw)
```

---

```{r echo=FALSE}
plot(p.sat_raw)
```

---

```{r echo=FALSE}
plot(p.time_raw)
```

###**Standardized** metrics show our converted values before their summarized by task.


```{r echo=FALSE}


  df_summarised %>%
    filter(group==1) %>%
    mutate(vjust_value=ifelse(point_est.nps<6,-.4,1.4)) %>%
    mutate(point_est.z=(point_est.z - .5) * 200)%>%
    mutate(lowerci.z=(lowerci.z- .5 )* 200)%>%
    mutate(upperci.z=(upperci.z- .5 )* 200)%>%
    ggplot(aes(x=Measure, y=point_est.z,fill=task_named,ymin=lowerci.z, ymax=upperci.z)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    coord_cartesian(ylim=c(-100,100)) +
    geom_errorbar(position=position_dodge(), stat="identity",color="gray",width=.2) +
    #geom_abline(intercept=.5,slope=0, color = "gray",linetype = 2, size=2) +
    geom_text(aes(label = round(point_est.z,0),hjust = 2,vjust=vjust_value,y=0), size = 3, position = "identity",color="black") +
    # scale_y_continuous(breaks=c(0:3)) +
    labs(x="", y="Standard score") +
    ggtitle(label = "Standardized Subscores for Tasks",
            subtitle = "Confidence Intervals at 90%") +
    ggthemes::theme_tufte(base_family="GillSans") + 
    scale_fill_manual(values=colpal)+
    theme(
      axis.text.x = element_text(size = 12),
      axis.text.y = element_text(size = 15),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15),
      title = element_text(size = 15),
      legend.position="none") +
  facet_wrap(~task)

```


###Finally, we can view our combined task metrics.

```{r echo=FALSE}

df_task %>%
  filter(group==1) %>%
  mutate(vjust_value=ifelse(point_est.nps<6,-.4,1.4)) %>%
  ggplot(aes(x=task, y=point_est.nps,fill=task_named,ymin=lowerci.nps, ymax=upperci.nps)) +
  geom_bar(position=position_dodge(), stat="identity") +
  coord_cartesian(ylim=c(-100,100)) +
  geom_errorbar(position=position_dodge(), stat="identity",color="gray",width=.2) +
  #geom_abline(intercept=.5,slope=0, color = "gray",linetype = 2, size=2) +
  geom_text(aes(label = round(point_est.nps,0),hjust=2,vjust=vjust_value,y=0), size = 3, position = "identity") +
  labs(x="", y="SUM scores") +
  ggtitle(label = "SUM scores for each measure on all tasks",
          subtitle = "Confidence Intervals at 90%") +
  scale_fill_manual(values=colpal)+
  guides(fill=guide_legend(title="Task Legend"))+
  ggthemes::theme_tufte(base_family="GillSans") + 
  theme(
    axis.text.x = element_text(size = 15)
    ) -> p.all_tasks_nps
plot(p.all_tasks_nps)

```